### 2021-06-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
fixes
Annotator table and graph

>>>>

\begin{table}[]
	\begin{tabular}{|l|l|l|l|l|l|}
		\hline
		Method     & Total Matches & Marked as Equal & Marked as Related & Marked as Unrelated & Not Marked \\ \hline
		Annotator1 & 40698         & 238             & 109               & 40351               & 0          \\ \hline
		Annotator2 & 40698         & 241             & 116               & 40341               & 0          \\ \hline
		Annotator3 & 40698         & 260             & 2103              & 38182               & 153        \\ \hline
		Annotator4 & 40698         & 225             & 62                & 40400               & 11         \\ \hline
	\end{tabular}
\end{table}
